Covariate and analysis of MSBB reprocessed counts Regressing out Diagnosis as well for TWAS

### 2020-05-22 code/prepscripts/MSBB_TranscriptNorm.Rmd
Trans DE MSBB

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn22092490';
activityName = 'Covariate and Diagnosis Regression';
activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective protien coding transcript level counts with CQN normalisation (IFG, STG, FP, PHG)';
thisFileName <- 'MSBB_TranscriptNorm.Rmd'
# Github link
thisRepo <- githubr::getRepo(repository = "Sage-Bionetworks/AD_TargetRank", ref="branch", refName='master')
thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/prepscripts',thisFileName))
```

>>>>

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn22092490';
activityName = 'Covariate and Diagnosis Regression';
activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective protien coding transcript level counts with CQN normalisation (IFG, STG, FP, PHG)';
thisFileName <- 'MSBB_TranscriptNorm.Rmd'
# Github link
thisRepo <- githubr::getRepo(repository = "Sage-Bionetworks/AD_TargetRank", ref="branch", refName='master')
thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/prepscripts/',thisFileName))
```
